---
title: "What Makes It Rain In San Francisco"
author: "C. G. Doherty"
date: "Friday, September 19, 2014"
output: ioslides_presentation
---

## US Weather History

---

## References

Descriptions:
https://gis.ncdc.noaa.gov/geoportal/catalog/search/resource/details.page?id=gov.noaa.ncdc:C00861
http://www.wmo.int/pages/prog/gcos/Publications/GCOS-144_en.pdf

Original Paper:
Menne, M.J., I. Durre, R.S. Vose, B.E. Gleason, and T.G. Houston, 2012a:  An overview 
of the Global Historical Climatology Network-Daily Database.  Journal of Atmospheric 
and Oceanic Technology, 29, 897-910.

Dataset Version:
Menne, M.J., I. Durre, B. Korzeniewski, S. McNeal, K. Thomas, X. Yin, S. Anthony, R. Ray, 
R.S. Vose, B.E.Gleason, and T.G. Houston, 2012: Global Historical Climatology Network - 
Daily (GHCN-Daily), Version 3.12-upd-2014091905.
ftp://ftp.ncdc.noaa.gov/pub/data/ghcn/daily/ghcnd_gsn.tar.gz

---

## Load Data

See loaddata.R

---

## Slide with R Code and Output

```{r}
summary(cars)
```

---

## Slide with Plot

```{r, echo=FALSE}
plot(cars)
```

